Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-13 paper/paper.qmd
Graph three

library(tidyverse)
library(palmerpenguins)
```

@@

Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(0.49, 3.99)
)

@@

Table_II <- data.frame(
  Job_satisfaction = c(5.64, 1.18),
  Belief_free_will = c(0.49, 3.99)
)

@@

print(Table_II)
```

Talk way more about it.

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

@@

Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

@@

Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)

@@

print(Table_II)
```
```{r}

# Load necessary libraries
library(ggplot2)
library(dplyr)

# Sample data
data <- data.frame(
  Country = rep(c("US", "Taiwan T1", "Taiwan T2"), each = 2),
  Value = c(5.28, 5.29, 3.99, 5.64, 3.99, 5.74), # Sample values ranging from 0 to 10
  Type = rep(c("Belief in Free Will", "Job Satisfaction"), 3)
)

# Plotting
ggplot(data, aes(x = Country, y = Value, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, 10)) +
  labs(x = "Country", y = "Scale") +
  theme_minimal() +
  scale_fill_manual(values = c("Belief in Free Will" = "blue", "Job Satisfaction" = "red")) # Custom colors for the bars

```
Talk way more about it.
